Escape Analysis and Specialization in a Tracing JIT

### 2010-09-26 talk/pepm2011/paper.tex
whoops

\authorinfo{Carl Friedrich Bolz \and Antion Cuni \and Maciek Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de XXX}

>>>>

\authorinfo{Carl Friedrich Bolz \and Antonio Cuni \and Maciek Fijałkowski \and Samuele Pedroni \and Armin Rigo}
           {Heinrich-Heine-Universität Düsseldorf, STUPS Group, Germany XXX}
           {cfbolz@gmx.de XXX}
